Detecting threats of violence in online discussions

### 2016-02-10 submission.tex
Added some text to intro and data set

@@

@@

\section{Introduction}
Threats of violence is an increasingly common occurrence in online
discussions. It disproportionally affects women and minorities, often
to the point of effectively eliminating them from taking part in
discussions online. Moderators of social networks operate on such a
big scale that manually reading all posts is an insurmountable
task. Methods for automatically detecting threats could therefore
potentially be very helpful, both to moderators of social networks,
and to the members of those networks.

@@

\section{Previous work}

\section{Data set}

\section{Experiments}

@@

\section{Discussion}

>>>>

\usepackage{verbatim}
\usepackage{booktabs}

@@

\newcommand{\tov}{threat of violence}
\newcommand{\Tov}{Threat of violence}
\newcommand{\tovs}{threats of violence}
\newcommand{\Tovs}{Threats of violence}
\newcommand{\hugo}{Hugo Lewi Hammer}
\newcommand{\Dep}{Dependency parsing}
\newcommand{\dep}{dependency parsing}

\newcommand{\Ds}{The YouTube threat data set}
\newcommand{\ds}{the YouTube threat data set}

@@

\section{Introduction}
\label{sec:intro}
Threats of violence is an increasingly common occurrence in online
discussions. It disproportionally affects women and minorities, often
to the point of effectively eliminating them from taking part in
discussions online. Moderators of social networks operate on such a
big scale that manually reading all posts is an insurmountable
task. Methods for automatically detecting threats could therefore
potentially be very helpful, both to moderators of social networks,
and to the members of those networks.

@@

\section{Previous work}
\label{sec:prev}
There is little previous work specifically devoted to the detection of
threats of violence in text, however, there is previous work which
examines other types of closely related phenomena, such as
cyberbullying and hate-speech.

\section{The YouTube threat data set}
\label{sec:data}
The YouTube threat data set is comprised of user-written comments from
eight different YouTube videos \cite{hammer2014}. A comment
consists of a set of sentences, each of them manually annotated to be
either a \tov{} (or support for a \tov{}) or not. The data set
furthermore records the username\footnote{In 2013, YouTube changed its
  commenting system from using unique usernames, to using "real
  names", like Facebook and other sites \cite{youtube2013}. Some
  accounts, however, did not provide real names, so they continue to
  only be identified by their usernames.} of the user that posted the
comment. The eight videos that the comments were posted to cover religious and political topics like halal slaughter, immigration,
Anders Behring Breivik, Jihad, etc. \cite{hammer2014}. 
%The videos cover slightly different topics, the videos all contain the same
%type of discussions, namely of xenophobia and racism.

The \ds consists of 9,845 comments, comprised of 28,643
sentences, see table \ref{tab:dataset}. In total there are 402,673 tokens in the sentences in the
data set. There are 1,285 comments containing threats, and 1,384
sentences containing threats, as seen in table \ref{tab:dataset}.
\cite{hammer2014} report inter annotator agreement on this data
set to be 98~\%, as calculated on 120 of the comments, doubly
annotated for evaluation.

Figure \ref{fig:comments} contains examples of some comments containing
\tovs{} taken from the data set. The first line is the username or
name, and the subsequent lines are the sentences of the comment. An
empty line indicates the end of a comment. The sentences are annotated
with a number indicating whether they contain a \tov{} (1), or not
(0).

\begin{figure}[h]
\begin{verbatim}
timpa666
1    and i will kill every fucking muslim and arab!

NimsXdimensions
0    Need a solution?
1    Drop one good ol' nuke on that black toilet in Mecca.

Ammar Alozaibi
1    Funny, We will conquer you all in just few years, U will be
     my slave and your women will be my Sex Toy in Bed.

LegitZombieSlayer1
0     As long as i'm alive you'll have no victory.
1     I'll kill all you cunts

\end{verbatim}
\caption{Examples of comments from the data set.}
\label{fig:comments}
\end{figure}

\begin{table}
\begin{center}
\begin{tabular}{lrrr}
  %&   &   &   \\
  \toprule

  & Commments  & Sentences  & Users posting \\
  \midrule

  Total  & $9,845$  & $28,643$  & $5,483$  \\
  Threats  & $1,285$  & $1,384$  & $992$  \\
  \bottomrule

\end{tabular}
\end{center}
\caption{Number of comments, sentences and users in \ds{}}
\label{tab:dataset}
\end{table}

\section{Experiments}
\label{sec:exp}

@@

\section{Discussion}
\label{sec:disc}
